---
title: "Canada"
author: '11484265'
date: "`r Sys.Date()`"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
source('HMD.R')
source('statsCan.R')
```

## Population Overview

```{r pyr}
# pop pyramid
gg_pyramid_2023
```

- Bullet 1
- Bullet 2
- Bullet 3

## All in and out
:::::: {.columns}
::: {.column}
```{r in}
gg_grow_in
```
:::

::: {.column}
```{r out}
gg_grow_out
```
:::
::::::


## Age-Specific Fertility Rates

```{r ASFR2023}
# age specific fertility rates
gg_ASFR_2023
```


## Dependency Ratio
```{r}
gg_dep
```

## Dependency Ratio 2023
:::::: {.columns}
::: {.column}
```{r}
gg_dep_2023
```
:::

::: {.column}
```{r}
gg_imm_dep_2023
```
:::
::::::

## Historical Age Categories 2023

```{r}
gg_agecat
```

## Historical Age Categories 2023
:::::: {.columns}
::: {.column}
```{r}
gg_agecat_2023
```
:::

::: {.column}
```{r}
gg_imm_agecat_2023
```
:::
::::::




## ASMR2020
```{r}
ASMR2020
```

## other rates
:::::: {.columns}
::: {.column}
```{r}
dx2020
```
:::

::: {.column}
```{r}
ex2020
```
:::
::::::



## Citation
HMD
HMD. Human Mortality Database. Max Planck Institute for Demographic Research (Germany), University of California, Berkeley (USA), and French Institute for Demographic Studies (France). Available at www.mortality.org (data downloaded on [Jan 7 2025]). 


STATS CAN

fert
Statistics Canada. (2024). Table 13-10-0418-01 Crude birth rate, age-specific fertility rates and total fertility rate (live births) [Data table].
https://doi.org/10.25318/1310041801-eng


growth
Statistics Canada. (2024). Table 17-10-0008-01 Estimates of the components of demographic growth, annual [Data table].  https://doi.org/10.25318/1710000801-eng


imm
Statistics Canada. (2024). Table 17-10-0014-01 Estimates of the components of international migration, by age and gender, annual [Data table].  https://doi.org/10.25318/1710001401-eng






